### 2022-09-15 input/proposal.tex
positioning

    (I)) or detects its possible blocking as follows:

@@

As a second step, detecting \processes must proactively purge the
system from their forwarded notifications. For instance in
Figure~\ref{fig:problemF}, $c$ detects the blocking of the staleness
notification $\delta_a$. It could broadcast $\delta_a$ in order to
acknowledge the staleness of its own $\alpha_a^3$ and inform
neighboring \processes that delivered it as well. Unfortunately, there
exists false positive in the blocking detection.
Lemma~\ref{lem:detector}'s proof shows that the detection at $y'$ does
not depend on $\delta_x$. Therefore $\delta_x$ may not exist but $y'$
still receives $\alpha_s$ after the delivery of $\delta_s$ from the
path it received and delivered
$\alpha_x$. Figure~\ref{fig:undoproblem} highlights this behavior. In
Figure~\ref{fig:undoproblemB}, $a$ does not delete its partition. In
Figure~\ref{fig:undoproblemF} and because of scoped broadcast, $c$
received the same series of messages as in
Figure~\ref{fig:problemF}. Yet, $c$ must assume the existence of
$\delta_a$ and act accordingly by forcing the staleness of its best
delivered message and disseminate this information to its neighbors.
To avoid flooding the system with false positive staleness
notifications, we reduce the scope of staleness notifications by
including only downstream \processes. In
Figure~\ref{fig:undoproblemF}, false positives would generate traffic
at $c$ and its children if it had any, without impacting $a$ and $b$.

>>>>

    (I)) or detects a possible blocking of the latter as follows:

@@

As a second step, detecting \processes must proactively purge the
system from their forwarded notifications. For instance in
Figure~\ref{fig:problemF}, $c$ detects the blocking of the staleness
notification $\delta_a$. It could broadcast $\delta_a$ in order to
acknowledge the staleness of its own $\alpha_a^3$ and inform
neighboring \processes that delivered it as well. Unfortunately, there
exists false positive in the blocking detection.
Lemma~\ref{lem:detector}'s proof shows that the detection at $y'$ does
not depend on $\delta_x$. Therefore $\delta_x$ may not exist but $y'$
still receives $\alpha_s$ after the delivery of $\delta_s$ from the
path it received and delivered
$\alpha_x$. Figure~\ref{fig:undoproblem} highlights this behavior. In
Figure~\ref{fig:undoproblemB}, $a$ does not delete its partition. In
Figure~\ref{fig:undoproblemF} and because of scoped broadcast, $c$
received the same series of messages as in
Figure~\ref{fig:problemF}. Yet, $c$ must assume the existence of
$\delta_a$ and act accordingly by forcing the staleness of its best
delivered message and disseminate this information to its neighbors.
To avoid flooding the system with false positive staleness
notifications, we reduce the scope of staleness notifications by
including only downstream \processes. In
Figure~\ref{fig:undoproblemF}, false positives would generate traffic
at $c$ and in turns, to its children if it had any. Nevertheless, this
would not affect $a$ nor $b$.
